---
title: "R games 期中報告"
output: html_notebook
---
組名：二二四all pass團

組員：陳奕璁、孫薇淇、鍾育晴

## Mid-Project: 

Given the 2016 Stat data set, estimate the final exam scores of 4 students who scores, say, 10, 30, 50, 70 (or more realistic scores of your interest) in the midterm Stat 2017.

According to an unidentified yet reliable source, the course grades given by instructor is roughly #A:#B:#C:#(D or E) ???1:3:3:3

Estimate the course grades of these 4 students. Please provide the assumptions and rationale of your estimation.

```{r}
#請往下到"Start:D"
```


###Import stat 2017 data 
```{r}
library(data.table)
#stat17<-fread('stat17noid.csv')
stat17<-fread('http://faculty.ndhu.edu.tw/~chtsao/ftp/stat17noid.csv')
colnames(stat17)<-c("year","mid")
stat17$year<-as.factor(stat17$year)
summary(stat17)
```
Data cleansing using subset command
```{r}
stat17[which(mid < 0)]
stat17<-subset(stat17,mid >= 0)
summary(stat17)
# You may also view the whole dataframe in the Environment pane ~ View(stat17)
```
Import stat 2016 data 
```{r}
stat16 <- fread('http://faculty.ndhu.edu.tw/~chtsao/ftp/stat2016.txt')
colnames(stat16)<-c("year","mid","final")
stat16$year<-as.factor(stat16$year)
head(stat16)   # Take a quick look of first few cases
summary(stat16)
```
Now we have two dataframes, stat2016(year, mid, final), stat2017(year,mid). 

##Where are we heading
Where are we now? What do we know? What do we want to know (but unknown now)?

> ~~Walk~~ Prog before you run. Think before you prog.

Some handy functions/commands for exploratory data analysis and data cleansing
```{r}
suppressMessages(library(dplyr)) # load package dplyr but suppress its messages
stat16.23<-filter(stat16, year == 2 | year == 3)
stat16.2<-filter(stat16,year==2 )
stat16.3<-filter(stat16,year==3)
summary(stat16.23)
```
```{r}
library(ggplot2)
scatter <- ggplot(data=stat16.23, aes(x = mid, y = final)) 
scatter + geom_point(aes(color=year, shape=year)) +
  xlab("midterm") +  ylab("final") +
  ggtitle("Midterm vs Final Plot (Stat16.23)")
```
More 
```{r}
smooth <- ggplot(data=stat16.23, aes(x=mid, y=final, color=year)) + 
  geom_point(aes(shape=year), size=1.5) + xlab("mid") + ylab("final") + 
  ggtitle("Scatterplot with smoothers")

# Linear model
smooth + geom_smooth(method="lm")

#Double check with console output
plot(final~mid, data=stat16.2)
m16.2<-lm(final~mid,data=stat16.2); summary(m16.2);
abline(m16.2)

```


```{r}
stat17.23<-filter(stat17, year == 2 | year == 3)
boxplot(mid~year, data=stat17.23)
stat17.2<-filter(stat17,year==2 )
stat17.3<-filter(stat17,year==3)
summary(stat17.2);summary(stat17.3)
par(mfrow=c(1,2));
hist(stat17.3$mid);hist(stat17.2$mid)
```

```{r}
smid17.2<-sort(stat17.2$mid, decreasing=TRUE)
ep<-rank(smid17.2)/47
summary(smid17.2);sd(smid17.2)
head(smid17.2)

smid17.2[27]
qnorm.ep<-qnorm(ep,39.79,31.68)
smid17.2
plot(smid17.2~qnorm.ep)
```

### Links and Referenes:

  - [Quick-R: Data management](http://www.statmethods.net/management/index.html)
  - [Data visualization with ggplot2](https://www.mailman.columbia.edu/sites/default/files/media/fdawg_ggplot2.html)
  - [Data Manipulation with  dplyr](https://www.r-bloggers.com/data-manipulation-with-dplyr/)
  - [Intro to dplyr](https://cran.rstudio.com/web/packages/dplyr/vignettes/introduction.html)



#Start:D


##以2016和2017的二三年級為主

###stat17.2
```{r}
smid17.2<-sort(stat17.2$mid, decreasing=TRUE)
ep<-rank(smid17.2)/47
summary(smid17.2);sd(smid17.2)
```

```{r}
head(smid17.2)
```

```{r}
qnorm.ep<-qnorm(ep,39.79,31.68)
smid17.2
```

```{r}
plot(smid17.2~qnorm.ep)
```

###stat17.3
```{r}
smid17.3<-sort(stat17.3$mid, decreasing=TRUE)
ep<-rank(smid17.3)/10
summary(smid17.3);sd(smid17.3)
```

```{r}
head(smid17.3)
```

```{r}
qnorm.ep<-qnorm(ep,39.79,31.68)
smid17.3
```

```{r}
plot(smid17.3~qnorm.ep)
```

###stat16.2
```{r}
smid16.2<-sort(stat16.2$mid, decreasing=TRUE)
ep<-rank(smid16.2)/42
summary(smid16.2);sd(smid16.2)
```
```{r}
head(smid16.2)
```
```{r}
qnorm.ep<-qnorm(ep,39.79,31.68)
smid16.2
```
```{r}
plot(smid16.2~qnorm.ep)
```

###stat16.3
```{r}
smid16.3<-sort(stat16.3$mid, decreasing=TRUE)
ep<-rank(smid16.3)/15
summary(smid16.3);sd(smid16.3)
```
```{r}
head(smid16.3)
```
```{r}
qnorm.ep<-qnorm(ep,39.79,31.68)
smid16.3
```
```{r}
plot(smid16.3~qnorm.ep)
```

##others

```{r}
smooth <- ggplot(data=stat16.23, aes(x=mid, y=year, color=year)) + 
  geom_point(aes(shape=year), size=1.5) + xlab("mid") + ylab("year") + 
  ggtitle("Scatterplot with smoothers - stat16.23")
# Linear model
smooth + geom_smooth(method="lm")

smooth <- ggplot(data=stat17.23, aes(x=mid, y=year, color=year)) + 
  geom_point(aes(shape=year), size=1.5) + xlab("mid") + ylab("year") + 
  ggtitle("Scatterplot with smoothers - stat17.23")
# Linear model
smooth + geom_smooth(method="lm")
```
```{r}
smooth <- ggplot(data=stat16.23, aes(x=final, y=year, color=year)) + 
  geom_point(aes(shape=year), size=1.5) + xlab("final") + ylab("year") + 
  ggtitle("Scatterplot with smoothers")
# Linear model
smooth + geom_smooth(method="lm")
```

```{r}
smid17.23<-sort(stat17.23$mid, decreasing=TRUE)
ep<-rank(smid17.23)/57
summary(smid17.23);sd(smid17.23)
```

```{r}
smid16.23<-sort(stat16.23$mid, decreasing=TRUE)
ep<-rank(smid16.23)/57
summary(smid16.23);sd(smid16.23)
```

```{r}
smid17<-sort(stat17$mid, decreasing=TRUE)
ep<-rank(smid17)/62
summary(smid17);sd(smid17)
```
```{r}
plot(smid17)

```


```{r}
#找出2016年期中期末之回歸線
lm(formula = stat16$final ~ stat16$mid)
#令x=期中成績,y=期末成績
#y=0.5517x+8.4448
```

```{r}
#Q1:找出四人期末分數 x=(15,30.5,41.19,58)
x<-c(15,30.5,41.19,58)
y<-0.5517*x+8.4448
y
```

```{r}
#Q2:分數A/B/C/D or E 比例約等於1:3:3:3 試問各成績區間?
#假設2016.2017總成績計算方式皆為40%期中+50%期末+10%平時成績(每人皆有) 缺考-10分
#先計算2016每人總成績
stat16a <- 0.4*stat16$mid + 0.5*stat16$final +10
sort(stat16a)

#成績A 63/10=6.3 為方便計算取6人
#成績B.C.D各為19人

```


```{r}
#由上述可知
room <- 0.4*x+0.5*y+10
room #四人2017學期總成績


```

#ANS:四人預測期末分數 16.7  25.2  31.1  40.4
#ANS:排列2016總成績後可知成績A區間為(100,77) B為[77,50) C為[50,33.1) D為[33.1,0]
#ANS:由此可知期中考的室友15分會得到D or E , 考30.5分會得C , 考41.19會得C 考58會得B

