---
title: "Work on Stat 2016/2017 exam data (rev)"
output: html_notebook
---
Rev note: Some (possibly) useful commands and experiments done in class are added. 

## Data management: 

Remove id data from 2017 data and output as a csv file. In addition,
I also randomly reorder the rows for anonymity. (R codes FYR/For Your Reference)
```{r Remove id}
#t<-matrix(scan("midstat2017m.csv"),ncol=3,byrow=T)
## The first column is id and intentionally left out
#exam16 <-data.frame(year=as.factor(t[,2]),mid=t[,3])
#exam16<-exam16[sample(nrow(exam16)),]
## Two different csv outputs
#write.csv(exam16, file = "stat17noid2.csv")
#write.table(exam16, file = "stat17noid.csv",row.names=FALSE, na="",col.names=FALSE, sep=" ")
```
Import stat 2017 data 
```{r}
library(data.table)
#stat17<-fread('stat17noid.csv')
stat17<-fread('http://faculty.ndhu.edu.tw/~chtsao/ftp/stat17noid.csv')
colnames(stat17)<-c("year","mid")
stat17$year<-as.factor(stat17$year)
head(stat17)
summary(stat17)
```
Data cleansing using subset command
```{r}
stat17[which(mid < 0)]
stat17<-subset(stat17,mid >= 0)
summary(stat17)
# You may also view the whole dataframe in the Environment pane ~ View(stat17)
```
```{r}
stat17[which(mid > 80)]
stat17<-subset(stat17,mid <= 80)
summary(stat17)
# You may also view the whole dataframe in the Environment pane ~ View(stat17)
```
Import stat 2016 data 
```{r}
stat16 <- fread('http://faculty.ndhu.edu.tw/~chtsao/ftp/stat2016.txt')
colnames(stat16)<-c("year","mid","final")
stat16$year<-as.factor(stat16$year)
head(stat16)   # Take a quick look of first few cases
summary(stat16)
```
```{r}
stat16[which(mid < 0)]
stat16<-subset(stat16,mid >= 0)
summary(stat16)
```
Now we have two dataframes, stat2016(year, mid, final), stat2017(year,mid). 

##Where are we heading
Where are we now? What do we know? What do we want to know (but unknown now)?

> ~~Walk~~ Prog before you run. Think before you prog.

Some handy functions/commands for exploratory data analysis and data cleansing
```{r}
suppressMessages(library(dplyr)) # load package dplyr but suppress its messages
stat16.23<-filter(stat16, year == 2 | year == 3)
stat16.2<-filter(stat16,year==2 )
stat16.3<-filter(stat16,year==3)
summary(stat16.23)
```


```{r}
#將2017的成績分類
stat17.23<-filter(stat17, year == 2 | year == 3)
stat17.2<-filter(stat17,year==2 )
stat17.3<-filter(stat17,year==3)
summary(stat17.23)
```
```{r}
library(ggplot2)
scatter <- ggplot(data=stat16.23, aes(x = mid, y = final)) 
scatter + geom_point(aes(color=year, shape=year)) +
  xlab("midterm") +  ylab("final") +
  ggtitle("Midterm vs Final Plot (Stat16.23)")
``````
More 



```{r}
stat17.23<-filter(stat17, year == 2 | year == 3)
boxplot(mid~year, data=stat17.23)
stat17.2<-filter(stat17,year==2 )
stat17.3<-filter(stat17,year==3)
summary(stat17.23)
par(mfrow=c(2,2));
hist(stat17.23$mid);hist(stat17.2$mid);hist(stat17.3$mid)
```


```{r}
smooth <- ggplot(data=stat16.23, aes(x=mid, y=final, color=year)) + 
  geom_point(aes(shape=year), size=1.5) + xlab("mid") + ylab("final") + 
  ggtitle("Scatterplot with smoothers")

# Linear model
smooth + geom_smooth(method="lm")

#Double check with console output
plot(final~mid, data=stat16.23)
m16.23<-lm(final~mid,data=stat16.23); summary(m16.23);
abline(m16.23)
m16.23$coef

```
```{r}
summary(stat17.23$mid)
sd(stat17.23$mid)
summary(stat16.23$mid)
sd(stat16.23$mid)
```
```{r}
x<-c(15.00, 30.50, 41.19, 58)
#2017  N(29.51, 20.09637^2)
#計算2017的期中百分比
pnorm(x, 29.51, 20.09637)
k<-c(0.3180282 , 0.4112158 , 0.9920863 , 0.7940476)
#將2017的成績換算成2016
#2016  N(46.07, 27.36125)
#計算2016的期中成績
xx<-qnorm(k, 46.07, 27.36125)
xx
#找2016期末成績
y<-0.5319059*(xx)+10.1265808
y
```
```{r}
#算2016學期總成績
Settlement<-0.35*stat16.23$mid+0.65*stat16.23$final
#算假設的2016學期總成績
SettlementA <-0.35*xx+0.65*y
SettlementA
#找出學期總成績的平均數跟標準差
summary(Settlement)
sd(Settlement)
#算A B C D 的標準
abcd<-c(9/10,6/10,3/10)

qnorm(abcd, 38.64, 23.06347)
#A>68.19703 , B>44.48306 , C>26.54550 , D<26.54550
#所以假設的分數，學期總成績必須大於31.72175
#31.72175-0.35*假設的期中分數=2016所需的期末成績
(26.54550-xx*0.35)/0.65


```
```{r}
#驗算期末成績是否有錯誤
cc<-(26.54550-xx*0.35)/0.65
sss <-0.35*xx+0.65*cc
sss
```

### Links and Referenes:

  - [Quick-R: Data management](http://www.statmethods.net/management/index.html)
  - [Data visualization with ggplot2](https://www.mailman.columbia.edu/sites/default/files/media/fdawg_ggplot2.html)
  - [Data Manipulation with  dplyr](https://www.r-bloggers.com/data-manipulation-with-dplyr/)
  - [Intro to dplyr](https://cran.rstudio.com/web/packages/dplyr/vignettes/introduction.html)


